Dynamic Transition Analysis with TIMES

### 2020-06-07 doc/2020-03-paper/acros.tex
added data + references
Former-commit-id: d21d3fa43c141a146410ddc02c412e9aeb411b66
Former-commit-id: 5dd078789f042d8cb1db3ad9cced13317e75feb5

\newacronym{<++>}{<++>}{<++>}
\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon Neutral Energy Research}
\newacronym{MARKAL}{MARKAL}{MARKet ALlocation}
\newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
\newacronym{IEEJ}{IEEJ}{The Institute of Energy Economics, Japan}
\newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
\newacronym{USC}{USC}{Ultra Supercritical Coal}
\newacronym{OM}{O\&M}{Operation and Maintenance Cost}
\newacronym{PEMFC}{PEM Fuel Cells}{Polymer Electrolyte Membrane Fuel Cells}
\newacronym{lcoe}{LCOE}{Levelized Cost of Electricity}
\newacronym{lng}{LNG}{Liquified Natural Gas}
%\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

>>>>

\newacronym{<++>}{<++>}{<++>}
\newacronym{I$^2$CNER}{I$^2$CNER}{International Institute for Carbon Neutral Energy Research}
\newacronym{MARKAL}{MARKAL}{MARKet ALlocation}
\newacronym{TIMES}{TIMES}{The Integrated MARKAL-EFOM System}
\newacronym{EDMC}{EDMC}{The Energy Data and Modelling Centre}
\newacronym{IEEJ}{IEEJ}{The Institute of Energy Economics, Japan}
\newacronym{CCS}{CCS}{Carbon Capture and Sequestration}
\newacronym{USC}{USC}{Ultra Supercritical Coal}
\newacronym{OM}{O\&M}{Operation and Maintenance Cost}
\newacronym{PEMFC}{PEMFC}{Polymer Electrolyte Membrane Fuel Cells}
\newacronym{lcoe}{LCOE}{Levelized Cost of Electricity}
\newacronym{lng}{LNG}{Liquified Natural Gas}
\newacronym{AEC}{AEC}{Alkaline Electrolyzer Cell}
\newacronym{PEMEC}{PEMEC}{Polymer Electrolyte Membrane Electrolyzer Cell}
\newacronym{SOEC}{SOEC}{Solid Oxide Electrolyzer Cell}
\newacronym{SOFC}{SOFC}{Solid Oxide Fuel Cell}
\newacronym{PWS}{PWS}{Photochemical Water Splitting}
%\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}

### 2020-06-07 doc/2020-03-paper/methods.tex
added data + references
Former-commit-id: d21d3fa43c141a146410ddc02c412e9aeb411b66
Former-commit-id: 5dd078789f042d8cb1db3ad9cced13317e75feb5

For time periods excluding the initial condition, the model can choose to deploy various renewables and base-load electricity generation technologies. The economic data and growth rates for these technologies are defined in tables \ref{existing-eco} and . The capital and \gls{OM} costs of offshore wind are significantly greater due to Japan's unusually deep seabed and the generally underdeveloped wind sector.

\begin{table}[!ht]
	\caption{Economic data for existing technologies.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.2\textwidth} p{0.16\textwidth} p{0.16\textwidth} p{0.16\textwidth}  p{0.1\textwidth} p{0.1\textwidth}}
		\hline
\textbf{Technology} & \textbf{Investment Cost} & \textbf{Fixed \gls{OM} costs} & \textbf{Variable \gls{OM} costs} & \textbf{Lifetime} & \textbf{Capacity Factor}\\
  & USD/kW & USD/kW & USD/MWh & Years & \\
\hline
Nuclear & 6317 & 121.13 & 2.36 & 60 & 0.90\\
Solar & 1307 (2017) & 15.19 & 0 & 25 & 0.14\\
Onshore Wind & 3454 (2017) & 136.37 & 0 & 25 & 0.4\\
Offshore Wind(Fixed) & 7772.73 & 341 & 0 & 25 & 0.44\\
Offshore Wind(Floating) & 12897 & 423 & 0 & 25 & 0.44\\
Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & 4h/24h \\
Natural Gas &  1079 & 14 & 2.54 & 10 & 0.55 \\
\gls{USC} & 3661 & 40.41 & 4.48 & 10 & 0.55 \\
\hline 
\end{tabularx}
\label{existing-eco}
\end{table}

@@

\subsection{Base scenarios}
%approach, goal, what are we hoping to learn
\begin{table}[!ht]
	\caption{Scenario definition.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.33\textwidth} p{0.33\textwidth} p{0.33\textwidth}}
\hline 
\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} \\
                 & \textbf{enabled} & \textbf{enabled} \\
                  \hline
%1               &   \xmark       &      \greencheck     \\ 
%2               & \xmark       &         \xmark       \\ 
%3               &   \greencheck     &      \greencheck     \\ 
%4               &   \greencheck     &         \xmark       \\
1               &   No       &      Yes     \\ 
2               &  No       &         No       \\ 
3               &   Yes     &      Yes     \\ 
4               &   Yes     &         No       \\

\hline
	\end{tabularx}
\label{scen-table}
\end{table}
\subsection{Sensitivity analysis}
%approach, goal, what are we hoping to learn

>>>>

For time periods excluding the initial condition, the model can choose to deploy various renewables and base-load electricity generation technologies. The economic data, such as capital costs, \gls{OM} costs, lifetime and capacity factors have been compiled from data sources into table \ref{existing-eco}. Dynamic trends are incorporated where available. The capital and \gls{OM} costs of offshore wind are significantly greater due to Japan's unusually deep seabed and the generally underdeveloped wind sector. Upper limits for growth rates are based on existing data, but with a generous margin of 5-20\%, as the trends in growth seen in the recent past may not represent the growth rates required to achieve the dramatic reduction in emissions we are aiming for.

\gls{PEMFC} \gls{PEMEC} \gls{AEC} \gls{USC} \gls{SOEC} \gls{SOFC} \gls{PWS}.

\begin{landscape}
\begin{longtable}{ |*{8}{c|} }
\caption{Economic data for modelled technologies.}\\
\hline
\textbf{Technology} & \textbf{Capital} & \textbf{Fixed} & \textbf{Variable} & \textbf{Lifespan} & \textbf{Capacity Factor/} & \textbf{Emission} & \textbf{Year} \\
\textbf{name} & \textbf{Cost} & \textbf{\gls{OM}} & \textbf{\gls{OM}} &  & \textbf{Efficiency} & \textbf{Coefficient} & \textbf{available} \\
 & MUSD/GW & MUSD/GW & MUSD/GWh & Years  &  & gCO$_2$/kWh  &  \\
\hline
\endhead  % header material
\hline
\endfoot  % footer material
\hline
\endlastfoot
\gls{USC} & 3661 & 40.41 & 4.48 & 40 & CF=0.55 & 943 & 2017 \\
\gls{lng} & 1079 & 14 & 2.54 & 30 & CF=0.55 & 599 & 2017 \\
Nuclear & 6317 & 121.13 & 2.36 & 60 & CF=0.6-0.95 & 943 & 2017 \\
Li-ion Storage & 1876 (2017) & 10 & 0.3 & 10 & Eff=0.86 & 52 & 2017 \\
 & 1446 (2025) &  &  &  &  & &  \\
Solar & 1307(2017) & 15.19 & 0  & 25 & CF=0.14 & 37 & 2017 \\
 & 1086(2040) & & & & &  & \\
 & 615(2050) & & & & & &  \\
Onshore Wind & 3454(2017) & 136.37 & 0 & 25 & CF=0.25(2017) & 20(2017) & 2017 \\
 & 3110(2040) &  &  &  & CF=0.3(2040) & 7(2040) &  \\
 & 2800(2050) &  &  &  & CF=0.35(2050) &  &  \\
Offshore Wind(Fixed) & 7772(2017) & 341 & 0 & 25 & CF=0.3(2017) & 25(2017) & 2017 \\
 & 5438(2040) &  &  & & CF=0.35(2040) & 11(2040) &  \\
 &  &  &  & & CF=0.4(2050) &  &  \\
Offshore Wind(Floating) & 12897(2017) & 423 & 0 & 25 & CF=0.35(2017) & 25(2017) & 2017 \\
 & 9023(2040) &  &  &  & CF=0.4(2040) & 11(2040)  &  \\
 &  &  &  &  & CF=0.45(2050) &  &  \\
CCS-LNG(90\%) & 5088(2022) & 33(2022) & 0.0631(2022) & 30 & CF=0.12-0.4(2017) & 42(2022) & 2022 \\
 & 2313(2050) & 14(2050) & 0.044(2050) &  & CF=0.35(2017) &  & \\
CCS-USC(90\%) & 6816(2023) & 84(2023) & 0.093(2023) & 40 & CF=0.27-0.3(2017) & 94.3(2022) & 2023 \\
 & 3552(2050) & 69(2050) & 0.058(2050) &  &  &  & \\
Emerging Solar & 4600(2017) & 15.19(2017) & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
 & 4600(2017) & 15.19 & 0 & 25 & Eff=0.22(2017) & 22(2017) & 2017 \\
 & 3822(2030) &  &  &  & Eff=0.25(2025) &  13(2040) &  \\
 & 2164(2035) &  &  &  & Eff=0.3(2030) &  &  \\
  & 1086(2040) &  &  &  &  &  &  \\
 & 615(2050) &  &  &  &  &  &  \\
  & 600(2051) &  &  &  &  &  &  \\
\gls{PEMFC} & 7399(2022) & 30.65 & 0.59 & 7 (CF=0.9) & Eff=0.6 & 0.408(2022) & 2022\\
 & 4000(2030) &  &  &  &  & 0.245(2030) &  \\
 & 3000(2030) &  &  &  &  & 0.245(2030) &  \\
\gls{AEC} & 1500(2022) & 6.87 & 0.0009 & 10(CF=0.9) & Eff=0.82 & 3.19 & 2022\\
 & 850(2030) &  &  &  &  & &  \\
\gls{PEMEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2022\\
 & 2200(2025) &  &  &  &  & 16(2050) &  \\
 & 1500(2030) &  &  &  &  &  &  \\
 & 1000(2035) &  &  &  &  &  &  \\
 & 500(2040) &  &  &  &  &  &  \\
\gls{SOEC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
\gls{SOFC} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2030\\
\gls{PWS} & 3500(2022) & 30.65 & 0.006 & 7 (CF=0.9) & Eff=0.78(2022) & 38.17(2022) & 2050\\
\label{eco}
\end{longtable}
\end{landscape}

\begin{table}[!ht]
%\begin{minipage}{\textwidth} 
	\caption{Installed capacity growth rate limits and capacity limits for existing technologies.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
		\hline
\textbf{Technology} & \textbf{Max. Annual} & \textbf{Net Capacity} \\
  & \textbf{Growth Rate}  & \textbf{Limit} (GW) \\
\hline
Nuclear (2027 onwards) & +5 reactors & 50 GW (with new tech)  \\
 & & 100 GW (without new tech)  \\
  & & (see Sec. \ref{scendef} ) \\
Solar & 40\% & 300 \\
Onshore Wind & 25\% & 3.75 (2017) \\
 &  & 15.3 (2020) \\
 &  & 39.9 (2030) \\
 &  & 57.0 (2040) \\
 &  & 114.0 (2100) \\
Offshore Wind(Fixed) & 20\% & 1 (2017) \\
 &  & 8.70 (2030) \\
 &  & 22.50 (2040) \\
 &  & 28.50 (2050) \\
 &  & 57.00 (2100) \\
Offshore Wind(Floating) & 20\% & 1 (2017) \\
 &  & 5.70 (2030) \\
 &  & 19.35 (2040) \\
 &  & 27.00 (2050) \\
 &  & 54.00 (2100) \\
Li-ion Storage & 30\% & None  \\
Natural Gas &  50\% & None \\
\gls{USC} & 50\% & None \\
\hline 
\end{tabularx}
\label{existing-gro}
%\end{minipage}
\end{table}

@@

\begin{table}[!ht]
	\caption{Installed capacity growth rate limits and capacity limits for emerging technologies.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.4\textwidth} p{0.3\textwidth} p{0.2\textwidth} }
		\hline
\textbf{Technology} & \textbf{Max. Annual} & \textbf{Net Capacity} \\
  & \textbf{Growth Rate}  & \textbf{Limit} (GW) \\
\hline
Emerging Solar & 40\% & None \\
All CCS, H$_2$ & 40\% (Year 1-5) & None \\
technologies & 60\% (Year 6-10) &  \\
 & 40\% (Year 11-15) & \\
 & 30\% (Year 16-) & \\
\hline 
\end{tabularx}
\label{emerging-gro}
\end{table}

\subsection{Base scenarios} \label{scendef}
%approach, goal, what are we hoping to learn

\begin{table}[!ht]
	\caption{Scenario definition.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{p{0.33\textwidth} p{0.33\textwidth} p{0.33\textwidth}}
\hline 
\textbf{Scenario}& \textbf{Emerging tech.} & \textbf{New nuclear} \\
                 & \textbf{enabled} & \textbf{enabled} \\
                  \hline
%1               &   \xmark       &      \greencheck     \\ 
%2               & \xmark       &         \xmark       \\ 
%3               &   \greencheck     &      \greencheck     \\ 
%4               &   \greencheck     &         \xmark       \\
1               &   No       &      Yes     \\ 
2               &  No       &         No       \\ 
3               &   Yes     &      Yes     \\ 
4               &   Yes     &         No       \\

\hline
	\end{tabularx}
\label{scen-table}
\end{table}

\subsection{Sensitivity analysis}
%approach, goal, what are we hoping to learn
